---
title: "Pilot Balance"
author: "Marco Medina"
date: "13/07/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Load libraries
pacman::p_load(here, dplyr, lubridate, tidyr, ggplot2, ggthemes, scales, readr,
               knitr, fixest, modelsummary, vtable)
```


```{r jobs_data}
# Load jobs_data.csv
jobs_data <- read_csv(here("01_Data", "03_Working", "jobs_data.csv"))
```

## Jobs Pilot

1. We started the pilot on 28/06/2022 with case files entered on 27/06/2022.

2. **Phase 1**. The first and a half week, we only assigned case files to the control group (A1), and the citatorio with encouragement group (B2).

3. **Phase 2**. For case files entered after 07/07/2022, we assigned them to the control group (A1), the citatorio with encouragement treatment arm (B2), and the citatorio with encouragement plus calculator treatment arm (C2).

```{r balance_table, results='asis'}
jobs_balance <- jobs_data %>%
  mutate(mujer = as.numeric(sexo == "MUJER"),
         jornada_diurna = as.numeric(jornada == "DIURNA"),
         pago_quincenal = as.numeric(frecuencia_cobro == "QUINCENAL"),
         abogado_ingresa = as.numeric(abogado_ingresa)) %>%
  select(accion_principal, edad, mujer, jornada_diurna, trabajador_base,
         pago_quincenal, horas_sem, salario_diario, antig_dias,
         abogado_ingresa, tratamiento, avg_amount_settlement, prob_getting_zero,
         avg_amount_payment)

sumtable(jobs_balance,
         group = "tratamiento", 
         group.test = T,
         out = "latex",
         title = "Balance Table - Jobs Pilot")
```

## Variable definition
* **accion_principal**: main claim dummy, where 1 means reinstatement.
* **edad**: worker's age.
* **mujer**: gender dummy, where 1 means woman.
* **jornada_diurna**: shift type dummy, where 1 means day shift.
* **trabajador_base**: worker type dummy, where 1 means "trabajador de confianza" (domestic worker, manager, director, personal driver, etc.)
* **pago_quincenal**: wage periodicity dummy, where 1 means biweekly payments.
* **horas_sem**: weekly working hours.
* **salario_diario**: daily wage.
* **antig_dias**: tenure in days.
* **abogado_ingresa**: dummy where 1 means the lawyer filed the lawsuit.
* **avg_amount_settlement**: calculator estimate for the amount paid in case of settlement.
* **prob_getting_zero**: calculator estimate for the probability of getting paid zero in case of laudo.
* **avg_amount_payment**: calculator estimate for the amount paid in case of laudo.

\clearpage

```{r balance_table_ph_1, results='asis'}
jobs_balance_ph_1 <- jobs_data %>%
  filter(date_mx < date("2022-07-06")) %>%
  mutate(mujer = as.numeric(sexo == "MUJER"),
         jornada_diurna = as.numeric(jornada == "DIURNA"),
         pago_quincenal = as.numeric(frecuencia_cobro == "QUINCENAL"),
         abogado_ingresa = as.numeric(abogado_ingresa)) %>%
  select(accion_principal, edad, mujer, jornada_diurna, trabajador_base,
         pago_quincenal, horas_sem, salario_diario, antig_dias,
         abogado_ingresa, tratamiento, avg_amount_settlement, prob_getting_zero,
         avg_amount_payment)

sumtable(jobs_balance_ph_1,
         group = "tratamiento", 
         group.test = T,
         out = "latex",
         title = "Balance Table - Phase 1")
```

```{r balance_table_ph_2, results='asis'}
jobs_balance_ph_2 <- jobs_data %>%
  filter(date_mx >= date("2022-07-06")) %>%
  mutate(mujer = as.numeric(sexo == "MUJER"),
         jornada_diurna = as.numeric(jornada == "DIURNA"),
         pago_quincenal = as.numeric(frecuencia_cobro == "QUINCENAL"),
         abogado_ingresa = as.numeric(abogado_ingresa)) %>%
  select(accion_principal, edad, mujer, jornada_diurna, trabajador_base,
         pago_quincenal, horas_sem, salario_diario, antig_dias,
         abogado_ingresa, tratamiento, avg_amount_settlement, prob_getting_zero,
         avg_amount_payment)

sumtable(jobs_balance_ph_2,
         group = "tratamiento", 
         group.test = T,
         out = "latex",
         title = "Balance Table - Phase 2")
```

